\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-07-10 manuscript/main.tex
update the changes

Furthermore, in Table \ref{tab:entry_effect_robustness_2}, The entry of Lianjia's offline stores significantly shortens the transaction period for the moderate HHI group by about 5\%. Conversely, this effect is not significant in the lower HHI group and higher concentration group. This pattern suggests that when the market is highly competitive, Lianjia is not able to shorten the transaction period and in highly concentrated markets, Lianjia is also unable to use its information advantage to shorten the transaction period. Regarding price concessions, the entry of Lianjia's offline stores does not have a significant effect in the moderate HHI group initially. However, the entry of offline stores have no influence on other groups. Overall, the results suggest that the entry of offline stores has a very limited influence on consumers' welfare but can help the brokerage earn more profit. Additionally, the entry of Lianjia's offline stores can help the brokerage attract more sellers and, consequently, find more buyers in the market, thereby increasing the brokerage's informational advantage. In the Appendix we also conducted the robustness check by classifying the group by matured market and less matured market.

@@

Appendix Figure \ref{fig:treatment_consolidation} illustrates the distribution of income across the treatment and control groups. Prior to the intervention, the two groups exhibit parallel trends, indicating no significant differences. The treatment effect becomes significant only after the first period, aligning with our empirical findings. We conducted a placebo test, as illustrated in Figure \ref{fig:placebo_concession_plat} like our previous estimation of the offline store expansion. The test result also shows that there is no other confounding factors affecting our analysis.

@@

>>>>

Furthermore, in Table \ref{tab:entry_effect_robustness_2}, The entry of Lianjia's offline stores significantly shortens the transaction period for the moderate HHI group by about 5\%. Conversely, this effect is not significant in the lower HHI group and higher concentration group. This pattern suggests that when the market is highly competitive, Lianjia is not able to shorten the transaction period and in highly concentrated markets, Lianjia is also unable to use its information advantage to shorten the transaction period. Regarding price concessions, the entry of Lianjia's offline stores does not have a significant effect in the moderate HHI group initially. However, the entry of offline stores have no influence on other groups. Overall, the results suggest that the entry of offline stores has a very limited influence on consumers' welfare but can help the brokerage earn more profit. Additionally, the entry of Lianjia's offline stores can help the brokerage attract more sellers and, consequently, find more buyers in the market, thereby increasing the brokerage's informational advantage. In the Appendix we also conducted the robustness check by classifying the market with low and high nighttime light areas and the results are reported in Appendix Table \ref{tab:robustness_nighttime_light_entry}.

@@

Appendix Figure \ref{fig:treatment_consolidation} illustrates the distribution of income across the treatment and control groups. Prior to the intervention, the two groups exhibit parallel trends, indicating no significant differences. The treatment effect becomes significant only after the first period, aligning with our empirical findings. We conducted a placebo test, as illustrated in Figure \ref{fig:placebo_concession_plat} like our previous estimation of the offline store expansion. The test result also shows that there is no other confounding factors affecting our analysis. In the Appendix Table \ref{tab:robustness_nighttime_light_consolidation}, we also classified the samples to low and high nighttime light areas, and the results show that our results are robust.

@@

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check for Offline Expansion Effect Using Nighttime Lights}
      \label{tab:robustness_nighttime_light_entry}
      \input{../result_tables/entry_light_robustness.tex}

\subsection{Robustness Check by Dividing the Samples to Low and High Nighttime Lights} \label{subsec:nighttime_light_robustness_check}

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check for Platform Consolidation Effect Using Nighttime Lights}
      \label{tab:robustness_nighttime_light_consolidation}
      \input{../result_tables/plat_light_robustness.tex}
